Appendix

### 2023-11-16 manuscript/manuscript.Rmd
Further update to document.

The result is shown in Figure \ref{fig:shifted-distributions}. For each distribution, transformation parameter $\hat{\lambda}$ varies with $d_{\text{shift}}$ and $d_{\text{scale}}$ when estimated using the original definitions.
In contrast, estimation of $\lambda$ using invariant power transformations was invariant to $d_{\text{shift}}$ and $d_{\text{scale}}$. 
While the effect of location on the estimated value of $\lambda$ using conventional power transformations is noticeable, scale also affects $\lambda$ for features that are not normally distributed.
The figure also shows that estimated $\lambda$ for Box-Cox power transformations in left-skewed distributions diverges from that found for invariant Box-Cox power transformations.

@@

Let us randomly draw $m_d=100$ asymmetric generalised normal distributions. Each distribution is parametrised with a randomly chosen skewness parameter $\alpha \sim U\left(0.01, 0.99\right)$ and shape parameter $\beta \sim U\left(1.00, 5.00 \right)$. Location and scale parameters are set as $\mu = 0$ and $\sigma = 1$, respectively. $n = \lceil 10^\gamma \rceil$ values are then randomly drawn, with $\gamma \sim U\left(2, 4\right)$. That is between $100$ and $10000$ values are drawn to create $\mathbf{X}_i$.

@@

```{=latex}
\begin{equation}
\left\{ \hat{k}_1, \hat{k}_2 \right\} = \argmin_{k_1, k_2} \sum_{i=1}^{m_d} \sum_{j=1}^{m_{out}} \left| \hat{\lambda}^r \left(\mathbf{X}_{i, j}; k_1, k_2 \right) - \hat{\lambda}_{0} \left(\mathbf{X}_i \right) \right|
\end{equation}
```
The double sum in right-hand side of the above equation can be considered as the loss that should be minimised.
Minimisation is performed using the `sbplx` algorithm implemented in the `nloptr` package for R [@Rowan1990-sn; @Ypma2022-tc].

@@

@@

```{r optimised-weighting-function-parameters, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Robustness of power transformations after optimising weighting function parameters. ",
  "The distribution of errors, i.e. the difference between robustly fitted $\\hat{\\lambda}^r$ ",
  "and expected $\\hat{\\lambda}_{0}$ found in the absence of outliers, is shown for 1000 randomly ",
  "parametrised asymmetric generalised normal distributions with up to 10% outliers on either side ",
  "of the distribution. The top and bottom panel show errors for the shift-sensitive Box-Cox transformation, ",
  "and shift-sensitive Yeo-Johnson transformation, respectively. ",
  "In each panel, the error distribution for the non-robust transformation is shown to the left ",
  "for comparison with different weighting methods. ",
  "Note that a square root transformation was used along the $y$-axis. Median errors are shown above each distribution."
)

.plot_optimised_weighting_function_parameters(
  plot_theme = plot_theme,
  manuscript_dir = manuscript_dir)
```

>>>>

The result is shown in Figure \ref{fig:shifted-distributions}. For each distribution, transformation parameter $\hat{\lambda}$ varies with $d_{\text{shift}}$ and $d_{\text{scale}}$ when estimated using the original definitions.
In contrast, estimation of $\lambda$ using invariant power transformations was invariant to $d_{\text{shift}}$ and $d_{\text{scale}}$. 
While the effect of location on the estimated value of $\lambda$ using conventional power transformations is noticeable, scale also affects $\lambda$ for features that are not normally distributed.
Figure \ref{fig:shifted-distributions} also shows that estimated $\lambda$ for Box-Cox power transformations in left-skewed distributions diverges from that found for invariant Box-Cox power transformations.

@@

Let us randomly draw $m_d=100$ asymmetric generalised normal distributions.
Each distribution is parametrised with a randomly chosen skewness parameter $\alpha \sim U\left(0.01, 0.99\right)$ and shape parameter $\beta \sim U\left(1.00, 5.00 \right)$.
Location and scale parameters are set as $\mu = 0$ and $\sigma = 1$, respectively.
$n = \lceil 10^\gamma \rceil$ values are then randomly drawn, with $\gamma \sim U\left(2, 4\right)$, i.e., between $100$ and $10000$ values are drawn to create $\mathbf{X}_i$.

@@

```{=latex}
\begin{equation}
\left\{ \hat{k}_1, \hat{k}_2 \right\} = \argmin_{k_1, k_2} \sum_{i=1}^{m_d} \sum_{j=1}^{m_{out}} \left| \hat{\lambda}^r \left(\mathbf{X}_{i, j}; k_1, k_2 \right) - \hat{\lambda}_{0} \left(\mathbf{X}_i \right) \right|
\end{equation}
```
The double sum in right-hand side of the above equation can be considered as the loss that should be minimised.
As mentioned earlier, transformation parameters are estimated using the BOBYQA algorithm for derivative-free bound constraint optimisation [@Powell2009-zb] through maximum likelihood estimation.

@@

```{r include = FALSE, eval = FALSE}
# This writes the lookup table for two-sided weighting parameters.
# power.transform package.
load(file = "./R/sysdata.rda")

two_sided_function_parameters <- .get_optimised_weighting_function_parameters(
  manuscript_dir = manuscript_dir,
  side = "both"
)

@@

```{r optimised-weighting-function-parameters, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Robustness of power transformations after optimising weighting function parameters. ",
  "The distribution of errors, i.e. the difference between robustly fitted $\\hat{\\lambda}^r$ ",
  "and expected $\\hat{\\lambda}_{0}$ found in the absence of outliers, is shown for 1000 randomly ",
  "parametrised asymmetric generalised normal distributions with up to 10% outliers on either side ",
  "of the distribution. The top and bottom panel show errors for the invariant Box-Cox ",
  "and invariant Yeo-Johnson transformations, respectively. ",
  "In each panel, the error distribution for the non-robust transformation is shown to the left ",
  "for comparison with different weighting methods. ",
  "Note that a square root transformation was used along the $y$-axis. Median errors are shown above each distribution."
)

.plot_optimised_weighting_function_parameters(
  plot_theme = plot_theme,
  manuscript_dir = manuscript_dir
)
```

### 2023-11-16 manuscript/manuscript_appendix.Rmd
Further update to document.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  eval = TRUE,
  fig.align= "center")

# Allow for defining figure captions within a chunk.
knitr::opts_knit$set(
  eval.after = "fig.cap")

require(power.transform)
require(ggplot2)
require(patchwork)
require(data.table)
require(latex2exp)
require(coro)
require(paletteer)
require(robustHD)
require(modeldata)

manuscript_dir <- file.path("C:/Users/alexz/Documents/GitHub/power.transform/manuscript")
source(file.path(manuscript_dir, "simulations.R"))
source(file.path(manuscript_dir, "plots.R"))

# Base font size.
base_size <- 10

# Set general theme.
plot_theme <- ggplot2::theme_light(base_size=base_size)
plot_theme$plot.title$size <- ggplot2::rel(1.0)
plot_theme$strip.background <- ggplot2::element_blank()
plot_theme$strip.text$colour <- NULL
plot_theme$plot.margin <- grid::unit(c(2, 2, 2, 2), "points")

parse_mean_sd_latex <- function(mu, sigma, digits=2L){
  return(paste0(
    "$", round(mu, digits=digits), " \\pm ", round(sigma, digits=digits), "$"
  ))
}
```
